%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arvind Saripalli} % Your name
\address{{arvindssaripalli@gmail.com} \tab{} \underline{\href{https://www.linkedin.com/in/arvindsaripalli/}{{Linkedin}}} \underline{\href{https://github.com/arvindsaripalli}{Github}}}
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of California, San Diego} \hfill {\em Sept 2017 - June 2020} 
\\ B.S. Computer Science \hfill { GPA: Cum. 3.9, Major 4.0 }
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Accel Robotics}{January 2018 - September 2018}{Software Engineering Intern}{}
\item Integrated Face and Object Detection into a real-time cashierless store using Convolution Neural Networks. Showcased demo to key investors and board members.
\item Developed an E2E Product Detection pipeline that was integrated into a real-time grab-and-go store.
\item Built a Network Video Recorder with Square API to automatically create and augment  video data.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Gravalabs}{September 2016 - August 2017}{Software Engineering Intern}{}
\item Developed a hybrid webapp for drug discovery with the Ionic/Angular framework.
\item Developed and integrated user API methods with webapp using AWS lambda.
\item Helped design the full stack of the Medzii drug discovery platform.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Research EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{UCSD Statistical Visual Computing Lab}{June 2018 - Present}{
Undergraduate Research Assistant}{Advised by Dr. Vasconcelos}
\item Aiming to classify plankton specimen by combining multiviews and pose data with image classification.
\item Attempting to improve low-shot learning computer vision problem in biological contexts.
\item Comparing 2D versus 3D image classification deep networks and publishing results in November 2018.
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Yonder Deep Robotics}{December 2017 - Present}{
Board Member, Software Team Lead}{}
\item Developing an Autonomous Underwater Vehicle (AUV) in conjunction with Scripps Institute of Oceanography. Received a \$10,000 NSF grant to develop affordable AUVs for Global Warming research.
\item Developed full AUV system with navigation control and wireless communication using Raspberry Pis and a serial radio connection.
\item Developing software to navigate AUVs Gyroscope/Depth/Acceleration sensor data and PID.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of Washington Medical Center}{June 2016 - August 2016}{Research Assistant}{}
\item Applied supervised learning models to CT data for error detection dosimetry quality assurance.
\item Wrote a paper detailing the project and submitted to the Siemens Research competition.
\end{rSubsection}

\end{rSection}

%--------------------------------------------------------------------------------------
\begin{rSection}{Skills}
\item Python: Deep Learning, Tensorflow, PyTorch, Numpy, OpenCV
\item Java, Javascript, C/C++ STL
\item Other: Shell Scripting, UNIX, Docker, AWS lambda, Git, SCRUM

\end{rSection}

\end{document}
