\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Arvind}{Saripalli}{
\href{mailto:arvindssaripalli@gmail.com}{arvindssaripalli@gmail.com} | 425.922.9961
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{UC San Diego}
\descript{BS in Computer Science}
\location{Expected June 2020 \\ Cum. GPA: 3.83 \\ Major GPA: 4.0}
\sectionsep



\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/arvindsaripalli}{\custombold{arvindsaripalli}} \\
LinkedIn:  \href{https://www.linkedin.com/in/arvindsaripalli/}{\custombold{arvindsaripalli}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Data Structures \\
Object Oriented Programming \\
UNIX/Software Tools \\
Algorithms/Systems Analysis \\
Discrete Math \\
\sectionsep

\section{Coursera}
Machine Learning \\
{\footnotesize \textit{\textbf{(Stanford University)}}} \\

\vspace{2mm}
Algorithms I \\
{\footnotesize \textit{\textbf{(Princeton University)}}} \\

\vspace{2mm}
Deeplearning \\
{\footnotesize \textit{\textbf{(Deeplearn.ai)}}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\location{Python}
\textbullet{} Scikit-learn \textbullet{} Tensorflow \textbullet{} Pytorch \\

\vspace{2mm}
\location{Java}
\textbullet{} Algorithms (USACO) \textbullet{} JUnit \\

\vspace{2mm}
\location{Javascript}
\textbullet{} Angular \textbullet{} Ionic Web Framework \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Accel Robotics}
\descript{| Software Engineering Intern }
\location{January 2018 – Present | La Jolla, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Building realtime Product and Face Detection system with Deep Neural Networks.
\item Optimizing detection and recognition system with CUDA.
\end{tightemize}
\sectionsep

\runsubsection{Gravalabs}
\descript{| Software Engineering Intern }
\location{September 2016 - August 2017 | Bellevue, WA}
\begin{tightemize}
\item Utilized the Ionic/Angular Javascript framework to develop a hybrid webapp for drug discovery.
\item Interacted with AWS lambda to integrate user APIs with webapp.
\item Helped design the full stack of the Medzii drug discovery and recommendation platform.
\end{tightemize}
\sectionsep

\runsubsection{Catalyst}
\descript{| Lead Programming Instructor}
\location{September 2015 - May 2017 | Redmond, WA}
\begin{tightemize}
\item Taught basic and advanced Python and Java to Middle School and High School students.
\item Created a Syllabus closely modelling AP Computer Science and Object Oriented Programming.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Yonder Deep Robotics}
\descript{| Navigation Software Team}
\location{December 2017 – Present | La Jolla, CA}
\begin{tightemize}
\item Undergraduate Research Robotics Team developing an AUV in conjunction with Grant Deane and Scripps Institute of Oceanography.
\item Developing software to navigate AUVs with IMU sensor data and Kalman Filtering.
\end{tightemize}
\sectionsep

\runsubsection{University of Washington Medical Center Radiation Oncology}
\descript{| Research Intern}
\location{June 2016 – August 2016 | Seattle, WA}
\begin{tightemize}
\item Utilized Python and the Scikit-learn Machine Learning Library.
\item Developed supervised learning models on CT data for error detection in EPID dosimetry.
\item Wrote a paper detailing the project and submited to the Siemens Research competition.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{\href{https://github.com/arvindsaripalli/Spotiflow}{Spotiflow}}
\descript{| Logical playlist organizer}
\begin{tightemize}
\item Built with Python, Last.fm and Spotify APIs for SDHacks 2017.
\item Used tensorflow to predict the genre of a song from track features.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXTRACURRICULARS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extracurricular} 
\vspace{2mm}
\begin{tightemize}
\item Member of Computer Science and Engineering Society.
\item Member of Data Science Student Society.
\item Former President of Exothermic Robotics and Captain of Team 10D.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}